---
title: "Exercise3&4"
author: "Rama Malhis (12585219)"
date: "2024-06-06"
output: html_document
---
## Aufgabe 3

b)

```{r}
library(tidyverse)
library(knitr)
library(gganimate)
library(transformr)
library(gifski)

names2022 <- read.csv("open_data_portal_2022.csv")
names2022%>% head(10)
names2023 <- read.csv("vornamen-muenchen-2023.csv")
names2023%>% head(10)
```

```{r}

typeof(names2022$Anzahl) #character
unique(names2022$Anzahl)

# The type is character because some of them have the value "4 oder weniger"
# The same by 'names2023'

names2022 <- names2022 %>%
  mutate(Anzahl = case_when(
    Anzahl == "4 oder weniger" ~ "4",
    TRUE ~ Anzahl
  )) %>%
  mutate(Anzahl = as.numeric(Anzahl))
names2022%>% head(10)

names2023 <- names2023 %>%
  mutate(Anzahl = case_when(
    Anzahl == "4 oder weniger" ~ "4",
    TRUE ~ Anzahl
  )) %>%
  mutate(Anzahl = as.numeric(Anzahl))
names2023%>% head(10)
# I replaced the value "4 or less" with just 4 to convert the variable to numeric
```

c)

```{r}
sum22 <- sum(names2022$Anzahl)
sum22
sum23 <- sum(names2023$Anzahl)
sum23
# 25199 babies were born in 2022, more than 24229 in 2023

```

d)

```{r}
names2022 <- names2022 %>%
  mutate(year = 2022)  
names2022%>% head(10)
names2023 <- names2023 %>%
  mutate(year = 2023)  
names2023%>% head(10)
```

e)

```{r}
combined_name <- bind_rows(names2022, names2023)
combined_name%>% head(10)
```

f)

```{r}
name_counts <- combined_name %>%
  group_by(Vorname) %>%
  summarize(total_count = sum(Anzahl) )%>%
  arrange(desc(total_count))


top_10_names <- name_counts %>%
  top_n(10, wt = total_count)

top_10_names %>%
  arrange(desc(total_count)) %>%
  kable(caption = "Top 10 Most Popular Names Across 2022 and 2023")
```

## Aufgabe 4
b)

```{r}
f_worked <- read.csv("Female weekly hours worked – OECD (2017).csv")
f_worked <- f_worked %>% 
  rename(  Avg_work_h = `Average.weekly.hours.worked..women..15....OECD.Labor.Force.Statistics..2017..`
)
f_worked%>% head(10)

```

c)

```{r}
#Datatset Name: Female weekly hours worked – OECD (2017)
#Link: https://github.com/owid/owid-datasets/tree/a24e0de2c034fe13140aab88ef7579a150151ce2/datasets/Female%20weekly%20hours%20worked%20%E2%80%93%20OECD%20(2017)

```

d)

Calculate the total mean of female weekly working hours for each country (2001-2016). Rank the countries where women work the longest in descending order.

This question is important to answer because it provides insights into the female work culture and working conditions in different countries over an extended period of time, making the statement more robust than the information for individual years.

e)

```{r}
f_worked_1 <- f_worked %>% 
  group_by(Entity) %>%
  summarise( total_ave_worked = mean(Avg_work_h)) %>%
  arrange(desc(total_ave_worked))

f_worked_1%>% head(10)
```

f)

```{r plot_female_work_hours, echo=FALSE, fig.cap="Figure: Average weekly working hours for women across different countries from 2001 to 2016", fig.height= 8, fig.width=10}

anim1 <- f_worked %>% ggplot( aes(x = Year, 
                         y =Avg_work_h)) +
  geom_point(aes(color = Entity)) +
  transition_time(Year)+
  labs(title = 'Year: {frame_time}',
       x = "Year",
       y = "Average Weekly Working Hours",
       caption = "Figur")

animated_plot <- animate(anim1, renderer = gifski_renderer(),
        heigh= 6, width= 8,
        unit= "in", res= 150)
anim_save("animated_work_hours.gif", animation = animated_plot)
animated_plot
```
